---
title: "ASNZ membership map"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    # pdf_document:
  html_document:
  # html_notebook:
    theme: spacelab
---

```{r setup, echo=FALSE}
# First load the town and suburb positions as saved by AIMSComponents.R
knitr::opts_chunk$set(echo=FALSE, cache=FALSE, error=TRUE)
load('townAndSuburbPositions')
# cairo_pdf()
```

```{r membersAddresses}
# Note: it is necesscary to first temporarily make the address list available to anyone with a link

# Get addresses of members
addList <- gsheet::gsheet2tbl('https://docs.google.com/spreadsheets/d/117-hjbsw2lKb-ywtbMZV7Yqvw_eo1j9j8kk07WuxUgw/edit#gid=7')
addList <- as.data.frame(addList)[, c('Address2','Address3a','Region','Status','Birth year')]
addList <- addList[tolower(addList$Status) %in% c('life member','member'),]
YoB <- addList$`Birth year`
addList <- addList[!is.na(addList$Address2) | !is.na(addList$Address3a),]
addList[is.na(addList$Address3a), 'Address3a'] <- addList[is.na(addList$Address3a), 'Address2']
```

```{r mergeWithLocations}
# Identify central town for each region (this will need to be amended if members join from new regions)
regCent <- data.frame(Region=c('Auckland','Bay of Plenty','Canterbury','Christchurch','Coromandel','Dunedin','Hawkes Bay',
                               'Manawatu','Nelson/Marlborough','Northland','Otago','Taranaki','Waikato','Wellington','West Coast'),
                      Reo=c('Ta\u304maki-makau-rau','Te Moana-a-Toi','Waitaha','Waitaha','Hauraki','\u14ct\u101kou','Te Matau-a-M\u101ui',
                            'Manawat\u16b','Te Tau Ihu o Te Waka a M\u101ui','Te Tai Tokerau','\u14ct\u101kou','Taranaki','Waikato',
                            'Te Whanganui-a-Tara','Te Tai Poutini'),
                      Centre=c('Auckland','Tauranga','Christchurch','Christchurch','Thames','Dunedin','Napier',
                               'Palmerston North','Nelson','Whangarei','Dunedin','New Plymouth','Hamilton','Wellington','Greymouth'),
                      stringsAsFactors=FALSE)
addList <- addList[addList$Region!='Overseas',]
addList <- merge(addList, regCent)
```

```{r regionalNumbers}
# Regional numbers
cexReg <- table(addList$Centre)
nosByReg <- data.frame(cex=cexReg, townPos[townPos$town %in% names(cexReg), -1])
nosByReg <- merge(regCent[!(regCent$Region %in% c('Christchurch','Dunedin')),], nosByReg, by.x='Centre', by.y='cex.Var1')
```

```{r theMap, fig.height=12, fig.cap='The area of the circle is proportional to the number of members in each region, and the circle is centred on the main city of the region.'}
par(xpd=TRUE, mar=rep(0,4))
myCol <- col2rgb('lightBlue')
maps::map('nz', fill=TRUE, col='lightGreen')
points(nosByReg[,'shape_X'], nosByReg[,'shape_Y'], pch=16, cex=sqrt(cexReg)/2,
       col=rgb(myCol[1], myCol[1], myCol[1], max=255, alpha=180))
points(nosByReg[,'shape_X'], nosByReg[,'shape_Y'], pch=1, cex=sqrt(cexReg)/2, col='darkBlue')
myAdj <- c(1,0,0,1,1,0,1,1,1,0,0,0,0) # this will need adjusting if new regions have been added above
myOff <- (1-2*myAdj)*0.22
for (i in 1:nrow(nosByReg))
{
  vOff <- 0.1
  text(nosByReg[i, 'shape_X']+myOff[i], nosByReg[i, 'shape_Y']+vOff,
       paste0(nosByReg[i, 'Region'], ' (', nosByReg[i, 'cex.Freq'], ')'),
       adj=myAdj[i], cex=0.9)
  text(nosByReg[i, 'shape_X']+myOff[i], nosByReg[i, 'shape_Y']-vOff, nosByReg[i, 'Reo'],
       adj=myAdj[i], cex=0.9)
  # text(nosByReg[i, 'shape_X']+myOff[i], nosByReg[i, 'shape_Y'],
  #      paste(nosByReg[i, 'Region'], nosByReg[i, 'Reo'], sep='\n'), adj=myAdj[i], cex=0.9)
}
```

## Age structure of membership

```{r ageStructure, fig.height=7, fig.cap='Age structure of the membership.'}
currYr <- date()
currYr <- as.integer(substring(currYr, nchar(currYr)-3))
ages <- currYr-YoB

par(las=1, xpd=TRUE, mgp=c(2.3, 0.8, 0))
tt <- hist(ages, main='', xlab='Age', ylab='Number of members')
tkMarks <- pretty(tt$counts)
axis(2, at=c(0, max(tkMarks)), labels=c('', max(tkMarks)))
lines(rep(c(min(tt$breaks), max(tt$breaks), NA), length(tkMarks)), rep(tkMarks, each=3), lty='dotted', col='grey30')
```

There are currently `r length(ages)` members of the New Zealand Anthroposophical Society, but the database holds the age of only `r length(ages[!is.na(ages)])` of these.  This is because the data was not collected initially, and thus those members for whom we do not have their age are likely to be older (in general) than those for whom we do have the data.  Thus, the age structure above is somewhat biased.
